Twists of supersymmetric gauge theories

### 2019-08-18 paper.tex
Making edits and corrections based on my conversation with Pavel.

\subsection{Symmetries in the Classical BV Formalism}

@@

\chris{todo: replace the argument here with an argument that only works in terms of the $I^{(i)}$.}

\begin{proof}
\chris{I'm leaving this for now, but Pavel wanted to rewrite this coordinate freely.}
Both are direct calculations using standard Clifford relations which cite below.
So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.  Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, (as in \cite{Guillen}):
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
\end{align*}
using the fact that 
\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
as in Theorem \ref{3_psi_thm}.  Making one more simplification using the Clifford relations, we have
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
\end{align*}
\end{proof}

In particular the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".  This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.  Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
\begin{align*}
\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
\end{align*}

@@

\begin{definition}
The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
where 
\begin{align*}
I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
\end{align*}
\end{definition}

We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.  Let us write $\d_{\mr{CE}}^\Gamma$ for the Chevalley-Eilenberg differential associated to the \emph{supertranslation algebra} $\CC^m \oplus \Pi \Sigma$, with bracket given by the pairing $\Gamma$.  We include the superscript $\Gamma$ here to distinguish this differential from the Chevalley-Eilenberg differential in the full super Poincar\'e algebra, which we will use below.

@@

\begin{proof}
\chris{fix to take care with signs, also we're removing that earlier lemma so this all needs changing.}
This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
\begin{align*}
\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_{Q_1} A\> + \<\lambda^*, \delta_{Q_1} \lambda\>, \<A^* , \delta_{Q_2} A\> + \<\lambda^*, \delta_{Q_2} \lambda\> \} \\
&= 2(\langle A^*, [\delta_{Q_1}, \delta_{Q_2}] A \rangle + \langle \lambda^*, [\delta_{Q_1}, \delta_{Q_2}] \lambda \rangle) \\
 &= 2(\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + \langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle  - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_1, \sd \dd \lambda)Q_2 - \frac 12(Q_2, \sd \dd \lambda)Q_1) \\
 &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
 &= - \d_{\mr{CE}}^\Gamma I^{(1)} -2\{S_{\mr{BV}} , I^{(2)}\}.
\end{align*}
Here we applied Lemma \ref{onshell_action_lemma} on the third line.
\end{proof}

The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.
\begin{lemma} \label{SUSY_rotation_invariance_lemma}
Let $I_{\mr{Poin}}$ be the interaction associated to the action of $\mf{iso}(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.  The functionals $I^{(1)}$ and $I^{(2)}$ are Poincar\'e invariant, meaning that
\begin{equation}\label{rot_invariance_eqn}
 \d_{\mr{Lie}} I^{(i)} = - \{I_{\mr{Poin}}, I^{(i)}\},
\end{equation}
for $i=1,2$.
\end{lemma}

\begin{proof}
First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since the Lie bracket between a supertranslation and an ordinary translation is always zero.  If we then consider the space $\Sigma$ of supertranslations as an $\so(n)$-module, 
\chris{...}
\end{proof}

@@

\begin{proof}
We can filter the complex $\clie^\bu(\mf A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{nd_MC} splits up as
\begin{align}
\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
&\quad + \d_{\mr{Lie}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
\end{align}
Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}. The remaining terms are those involving the action of supersymmetries.

@@

In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.  Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.  Indeed, we expand 
\begin{align*}
 \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + (123) \\
 &= \left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + (Q_2, \lambda^*)Q_1)\right\rangle + (123),
\end{align*}
where $(123)$ indicates symmetrization in $Q_1, Q_2, Q_3$.  We can simplify this expression by manipulating the first summand.  Indeed,
\begin{align*}
\left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*)\right\rangle &= 
\end{align*}
\chris{...}

@@

>>>>

\subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}

@@

We'll prove this lemma after first translating it into more convenient language: the terminology of the equivariant action functional, as introduced in Section \ref{symmetry_section}.  Our Lemma \ref{onshell_action_lemma} tells us that the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".  This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.  Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
\begin{align*}
\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
\end{align*}

@@

\begin{definition}
The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
where 
\begin{align*}
I^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
\end{align*}
\end{definition}

We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals, using the interpretation where 
\begin{align*}
I^{(1)}(Q) &= \<A^* , \delta_{Q} A\> + \<\lambda^*, \delta_{Q_1} \lambda\> \\
\text{and } I^{(2)}(Q_1,Q_2) &= \<\lambda^*, \delta^{(2)}_{Q_1,Q_2}\lambda\>.
\end{align*}
Let us write $\d_{\mr{CE}}^\Gamma$ for the Chevalley-Eilenberg differential associated to the \emph{supertranslation algebra} $\CC^m \oplus \Pi \Sigma$, with bracket given by the pairing $\Gamma$.  We include the superscript $\Gamma$ here to distinguish this differential from the Chevalley-Eilenberg differential in the full super Poincar\'e algebra, which we will use below.

@@

\chris{Pavel wants to replace these two proofs: first of Lemma \ref{onshell_action_lemma}, then of Lemma \ref{onshell_interaction_lemma}, with a single coordinate free argument.}
\begin{proof}[Proof of Lemma \ref{onshell_action_lemma}]
Both of the two statements are direct calculations using standard Clifford relations which cite below.
So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.  Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, (as in \cite{Guillen}):
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
\end{align*}
using the fact that 
\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
as in Theorem \ref{3_psi_thm}.  Making one more simplification using the Clifford relations, we have
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
\end{align*}
\end{proof}

\begin{proof}[Proof of Lemma \ref{onshell_interaction_lemma}]
The functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
\begin{align*}
\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_{Q_1} A\> + \<\lambda^*, \delta_{Q_1} \lambda\>, \<A^* , \delta_{Q_2} A\> + \<\lambda^*, \delta_{Q_2} \lambda\> \} \\
&= 2(\langle A^*, [\delta_{Q_1}, \delta_{Q_2}] A \rangle + \langle \lambda^*, [\delta_{Q_1}, \delta_{Q_2}] \lambda \rangle) \\
 &= 2(\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + \langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle  - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_1, \sd \dd \lambda)Q_2 - \frac 12(Q_2, \sd \dd \lambda)Q_1) \\
 &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
 &= - \d_{\mr{CE}}^\Gamma I^{(1)} -2\{S_{\mr{BV}} , I^{(2)}\},
\end{align*}
where we applied Lemma \ref{onshell_action_lemma} on the third line. \chris{note, we should be careful to make sure that the sign in the $\d_{\mr{CE}}^\Gamma I^{(1)}$ term is correct.}
\end{proof}

The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.  Let $\d^{\mr{rot}}_{\mr{CE}}$ denote the Chevalley Eilenberg differential in the super Lie algebra $\so(n) \ltimes \Pi \Sigma$.  The total Chevalley-Eilenberg differential, applied to a functional $F$ on the purely fermionic part of the super Poincar\'e algebra, is therefore the sum
\[\d_{\mr{CE}}(Q) = \d^\Gamma_{\mr{CE}}(Q) + \d^{\mr{rot}}_{\mr{CE}}(Q).\]

\begin{lemma} \label{SUSY_rotation_invariance_lemma}
Let $I_{\mr{rot}}$ be the interaction associated to the action of the Lie algebra $\mf{so}(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.  The functionals $I^{(1)}$ and $I^{(2)}$ are Poincar\'e invariant, meaning that
\begin{equation}\label{rot_invariance_eqn}
 \d^{\mr{rot}}_{\mr{CE}} I^{(i)} = - \{I_{\mr{rot}}, I^{(i)}\},
\end{equation}
for $i=1,2$.
\end{lemma}

\begin{proof}
If we consider the space $\Sigma$ of supertranslations as an $\so(n)$-module, 
\chris{...}
\end{proof}

@@

\begin{proof}
We can filter the complex $\clie^\bu(\mf A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{nd_MC} splits up as
\begin{align}
\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{CE}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
&\quad + \d_{\mr{CE}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
&\quad + \d_{\mr{CE}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
\end{align}
Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}. The remaining terms are those involving the action of supersymmetries.

@@

In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.  Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.  Indeed, we expand 
\begin{align*}
 \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + (123) \\
 &= \left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + (Q_2, \lambda^*)Q_1)\right\rangle + (123),
\end{align*}
where $(123)$ indicates symmetrization in the supercharges $Q_1, Q_2, Q_3$.  We can simplify this expression by manipulating the first summand.  Indeed,
\begin{align*}
\left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*)\right\rangle &= - \left\langle A^*\;,\; \Gamma(\lambda^*, \rho(\Gamma(Q_1,Q_2)) Q_3)\right\rangle - (\lambda^*, Q_3) g(A^*, \Gamma(Q_1,Q_2)).
\end{align*}
\chris{needs an argument, and care with signs.  Probably with the coordinate free argument above we'll have to include some lemmas on spinor manipulation that we can reference here.}  Thus, after symmetrization, we have shown that
\[\{I^{(1)}, I^{(2)}\}= - \left\langle A^*\;,\; \Gamma(\lambda^*, \rho(\Gamma(Q_1,Q_2)) Q_3)\right\rangle + (123),\]
which vanishes by Theorem \ref{3_psi_thm}.

@@

\chris{Pavel points out that we would like to know more, namely supersymmetry for theories with supersymmetric matter.  In order to prove this, we have to check :
\begin{enumerate}
 \item That the 4d chiral and 6d hyper multiplet are supersymmetric.
 \item That the coupling terms $I_{\mr{coupling}}$ between these multiplets and the vector multiplet satisfy $\{I_{\mr{coupling}}, I^{(i)}\} = 0$ for $i=1,2$ (the $I^{(i)}$ split into a term describing the action on the vector as above, plus a term describing the action on the matter, and in the bracket these must cancel.)
\end{enumerate}
This implies the same after dimensional reduction, which tells us supersymmetry for the remaining examples: 5d, 3d, and 2d with matter.}
